\Large{Adversarial Training against Systematic Uncertainty}

### 2016-09-29 tex/paper.tex
save

Systematic uncertainties in high energy physics represent our incomplete
knowledge in the simulation of physical processes or in the properties of the
detection apparatus. In effect, systematic uncertainties may cause variations in
the conditional distributions of the features used for training a predictive
model like a classifier, thereby altering its decisions and resulting efficacy.
In this paper, we repurpose adversarial training as a means to produce a pivotal
classifier which is invariant to variations of the nuisance parameters
describing the effects of systematic uncertainties. In the machine learning
context, this problem is closely related to those of domain adaptation and
enforcing fairness in classification. Following that line of work, the proposed
method can be regarded as generalization that also supports the continuous case,
which can be viewed as handling infinitely many domains or as enforcing fairness
over continuous features.

>>>>

In high energy physics, systematic uncertainties represent our incomplete
knowledge in the simulation of physical processes or in the properties of the
detection apparatus. In effect, these uncertainties typically cause variations
in the conditional distributions of the data, thereby altering the decisions
and resulting efficacy of a classifier trained from it. In this work, we
repurpose adversarial training as a means to learn a pivotal classifier which is
invariant to variations of the nuisance parameters describing the effects of
systematic uncertainties. In machine learning, this problem is closely related
to those of domain adaptation and enforcing fairness in classification.
Following that line of work, the proposed method can be regarded as
generalization that also supports the continuous case, which can be viewed as
handling infinitely many domains or as enforcing fairness over continuous
features.
